% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass{llncs}
%
\usepackage{makeidx}  % allows for indexgeneration
\usepackage{amssymb}  % packages for math symbols
\usepackage{isabelle,isabellesym} % packages for Isabelle-specific math symbols

\isabellestyle{it} % theory text in math-similar italics

%
\begin{document}
%
\frontmatter          % for the preliminaries
%
\pagestyle{headings}  % switches on printing of running heads

%
\mainmatter              % start of the contributions
%
\title{Computer-Formalizations of \\
	the Ontological Argument Using\\
	Intensional Higher-Order Modal Logic}
%
%\titlerunning{??}  % abbreviated title (for running head) also used for the TOC unless \toctitle is used
\author{David Fuenmayor\inst{1} \and Christoph Benzm\"uller\inst{2,1}}
%
%\authorrunning{??} % abbreviated author list (for running head)

%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{David Fuenmayor, Christoph Benzm\"uller}
%
\institute{Freie Universit\"at Berlin, Germany
%\email{davfuenmayor@gmail.com}
\and
University of Luxembourg, Luxembourg
%\email{c.benzmueller@gmail.com},\\ WWW home page:
%\texttt{http://christoph-benzmueller.de}
}

\maketitle              % typeset the title of the contribution

\begin{abstract}
	A computer-formalization in Isabelle/HOL of several variants of G\"odel's ontological argument is presented (as discussed in M. Fitting's textbook \emph{Types, Tableaus and G\"odel's God}). Fitting's work	introduces an intensional higher-order modal logic (by drawing on Montague/Gallin approach), which we shallowly embed here in classical higher-order logic (Isabelle/HOL). We then	utilize the embedded logic for the
	formalization of the ontological argument. In particular, Fitting's and Anderson's variants are verified and their claims confirmed. These variants aim to avoid the modal collapse, which has been criticized as an undesirable side-effect of Kurt G\"odel's (and Dana Scott's) versions of the ontological argument.
	\keywords{Automated Theorem Proving. Computational Metaphysics. Isabelle. Modal Logic.
	Intensional Logic. Ontological Argument}
\end{abstract}

\input{IHOML.tex}
\input{GoedelProof.tex}
\input{FittingProof.tex}
\input{AndersonProof.tex}

%
% ---- Bibliography ----
\bibliographystyle{abbrv}
\bibliography{FittingBook}


%\clearpage
%\addtocmark[2]{Author Index} % additional numbered TOC entry
%\renewcommand{\indexname}{Author Index}
%\printindex
%\clearpage
%\addtocmark[2]{Subject Index} % additional numbered TOC entry
%\markboth{Subject Index}{Subject Index}
%\renewcommand{\indexname}{Subject Index}
%\input{subjidx.ind}
\end{document}
