% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass{llncs}
%
\usepackage{makeidx}  % allows for indexgeneration
\usepackage{amssymb}  % packages for math symbols
\usepackage{isabelle,isabellesym} % packages for Isabelle-specific math symbols

\isabellestyle{it} % theory text in math-similar italics

%
\begin{document}
%
\frontmatter          % for the preliminaries
%
\pagestyle{headings}  % switches on printing of running heads

%
\mainmatter              % start of the contributions
%
\title{Types, Tableaus and G\"odel's God \\ in Isabelle/HOL}
%
%\titlerunning{??}  % abbreviated title (for running head) also used for the TOC unless \toctitle is used
\author{David Fuenmayor\inst{1} \and Christoph Benzm\"uller\inst{2,1}}
%
%\authorrunning{??} % abbreviated author list (for running head)

%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{David Fuenmayor, Christoph Benzm\"uller}
%
\institute{Freie Universit\"at Berlin, Germany
%\email{davfuenmayor@gmail.com}
\and
University of Luxembourg, Luxembourg
%\email{c.benzmueller@gmail.com},\\ WWW home page:
%\texttt{http://christoph-benzmueller.de}
}

\maketitle              % typeset the title of the contribution

\begin{abstract}
	A computer-formalization of the essential parts of Fitting's textbook
	\emph{Types, Tableaus and G\"odel's Go}d in Isabelle/HOL is
	presented. In particular, Fitting's (and Anderson's) variant of the ontological
	argument is verified and confirmed. This variant avoids the modal
	collapse, which has been criticized as an undesirable side-effect of Kurt G\"odel's (and
	Dana Scott's) versions of the ontological argument. Fitting's work
	is employing an intensional higher-order modal logic, which we
	shallowly embed here in classical higher-order logic. We then
	utilize the embedded logic for the formalization of Fitting's argument.
	\keywords{Automated Theorem Proving. Computational Metaphysics. Isabelle. Modal Logic. Ontological Argument}
\end{abstract}

\input{IHOML.tex}
\input{IHOML_Examples.tex}
\input{GoedelProof_P1.tex}
\input{GoedelProof_P2.tex}
\input{FittingProof.tex}
\input{AndersonProof.tex}

%
% ---- Bibliography ----
\bibliographystyle{abbrv}
\bibliography{FittingBook}


%\clearpage
%\addtocmark[2]{Author Index} % additional numbered TOC entry
%\renewcommand{\indexname}{Author Index}
%\printindex
%\clearpage
%\addtocmark[2]{Subject Index} % additional numbered TOC entry
%\markboth{Subject Index}{Subject Index}
%\renewcommand{\indexname}{Subject Index}
%\input{subjidx.ind}
\end{document}
